### 2018-05-02 paper/message-passing-design.tex
new figure

\begin{figure}[t]
  \includegraphics[width=\linewidth]{figures/file_exchange.pdf}
  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
\end{figure}

@@

% subsubsection exchanging_a_file (end)
\newcommand{\messagesize}{\ensuremath{s_m}}
\newcommand{\filesize}{\ensuremath{s_f}}
\newcommand{\headersize}{\ensuremath{s_{\mathcal{H}}}}

@@

To prevent \name from message size analysis attacks, the messages have a fixed size \messagesize.
As shown in the previous section~\ref{ssub:building_routes}, headers have a variable size \headersize per route (but \Hforward remains constant once the POR is established).
For this reason, file chunks have a fixed size per session: $\filesize = \messagesize - \headersize$.

>>>>

\begin{figure}[t]
  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
  \caption{\label{fig:file-exchange}A schematic of the creation and usage of PORs between Alice and Bob's e-squads.}
\end{figure}

@@

% subsubsection exchanging_a_file (end)
\newcommand{\messagesize}{\ensuremath{s_m}}
\newcommand{\filesize}{\ensuremath{s_{fc}}
\newcommand{\headersize}{\ensuremath{s_{\mathcal{H}}}}

@@

\commentAL{Is it good?}
In \name, whole messages, headers and file chunks are considered having a fixed size.
In reality, the message size \messagesize is indeed fixed to prevent \name from message size analysis attacks,
but the header size \headersize is variable, depending on the number of layers and the number of devices per layer.
File chunks would then have a size  inversely proportional to \headersize : $\filesize = \messagesize - \headersize$.

% To prevent \name from message size analysis attacks, the messages have a fixed size \messagesize.
% As shown in the previous section~\ref{ssub:building_routes}, headers have a variable size \headersize per route (but \Hforward remains constant once the POR is established).
% For this reason, file chunks have a fixed size per session: $\filesize = \messagesize - \headersize$.
